Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-04-29 thesis/paper/thesis.tex
added subsections for results
res
Added superscript and fixed some random letters at the end of scentences

\subsection{Research Questions} \label{rqs}
\begin{description}
\item[\textbf{RQ1:}] What drives API evolution?x
\item[\textbf{RQ2:}] To what extent can we reverse engineer API change decisions?
\end{description}

@@

%%Lehman's laws (!!!improve later)
An early study made in the area of software evolution suggests that changes to software must obey one of eight laws of software evolution \cite{lehman1980programs}. The laws presented in the study are 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conversation of Familiarities, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}. The study also outlines that these laws only apply to E-programs, which are programs that are ``change prone" and that ``mechanise a human or societal activity" \cite{lehman1980programs}.o

@@

\section{Results} \label{results}

>>>>

\subsection{Research Questions} \label{rqs}
\begin{description}
\item[\textbf{RQ1:}] What drives API evolution?
\item[\textbf{RQ2:}] To what extent can we reverse engineer API change decisions?
\end{description}

@@

%%Lehman's laws (!!!improve later)
An early study made in the area of software evolution suggests that changes to software must obey one of eight laws of software evolution \cite{lehman1980programs}. The laws presented in the study are 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conversation of Familiarities, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}. The study also outlines that these laws only apply to E-programs, which are programs that are ``change prone" and that ``mechanise a human or societal activity" \cite{lehman1980programs}.

@@

 \newpage
\section{RQ1} \label{results}
This section will cover the results.

\subsection{New}
Intro...

\subsubsection{axaudio}

%%Describe the change

%%Relate it to Categories

%%Relate it to Lehman

\subsubsection{axptz}

%%Describe the change

%%Relate it to Categories

%%Relate it to Lehman

\subsubsection{axstorage}

%%Describe the change

%%Relate it to Categories

%%Relate it to Lehman

\subsubsection{axserialport}

%%Describe the change

%%Relate it to Categories

%%Relate it to Lehman

\subsection{Modified}
Intro...

\subsubsection{axevent}

%%Describe the change

%%Relate it to Categories

%%Relate it to Lehman

\subsubsection{axhttp}

%%Describe the change

%%Relate it to Categories

%%Relate it to Lehman

\subsubsection{axparameter}

%%Describe the change

%%Relate it to Categories

%%Relate it to Lehman

\subsection{Removed}
Intro...

\subsubsection{Burst Mode}

%%Describe the change

%%Relate it to Categories

%%Relate it to Lehman

\subsection{General Trends}

Intro...

\subsubsection{Example Code}

%%Describe the change

%%Relate it to Categories

%%Relate it to Lehman

\subsubsection{Documentation}

%%Describe the change

%%Relate it to Categories

%%Relate it to Lehman

\subsubsection{Interfaces}

%%Describe the change

%%Relate it to Categories

%%Relate it to Lehman

\subsubsection{Error Handling}

%%Describe the change

%%Relate it to Categories

%%Relate it to Lehman

\subsubsection{3\textsuperscript{rd} Party}

%%Describe the change

%%Relate it to Categories

%%Relate it to Lehman

\section{RQ2}
Have a table with ours and hers
